Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-09-25 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
correct two variable names

df.C1.v.sum_eff_w$Id_RT_Good_selfEffect  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
df.C1.v.sum_eff_w$Id_RT_Self_valEffect   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
df.C1.v.sum_eff_w$Id_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Good_Other
df.C1.v.sum_eff_w$Id_RT_badslf_badoth <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Bad_Other

>>>>

df.C1.v.sum_eff_w$Id_RT_goodslf_goodoth  <- df.C1.V.sum_w$RT_Id_Good_Other - df.C1.V.sum_w$RT_Id_Good_Self
df.C1.v.sum_eff_w$Id_RT_goodslf_badslf   <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Good_Self
df.C1.v.sum_eff_w$Id_RT_goodoth_badoth <- df.C1.V.sum_w$RT_Id_Bad_Other - df.C1.V.sum_w$RT_Id_Good_Other
df.C1.v.sum_eff_w$Id_RT_badslf_badoth <- df.C1.V.sum_w$RT_Id_Bad_Self - df.C1.V.sum_w$RT_Id_Bad_Other
